---
title: "TMDB Movie - Data Visualisation"
author: "Enlik Tjioe"
date: "24 January 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Libraries
```{r}
library(ggplot2)
library(lubridate)
```

## 2. Kaggle Dataset
[TMBD 5000 Movie Dataset](https://www.kaggle.com/tmdb/tmdb-movie-metadata)

## 3. Pre-Processing Data
Workflow:

* Reading your data
* Take a peek at your data
* Inspect your structure of data
* Formulate questions (strategic business value)
* Answer questions efficiently

Data Visualization Data (csv, database, images) -> preprocessing -> eda (exploratory data analysis) -> visualization / plotting

### 3.1 Pre-processing
`mv` is a dataframe with 4803 observations and 20 variables
```{r}
mv <- read.csv("data_input/tmdb_5000_movies.csv", stringsAsFactors = FALSE)
# str(mv)

mv[,c("original_language", "status")] <- lapply(mv[,c("original_language", "status")], as.factor)
mv$release_date <- ymd(mv$release_date)
```

### 3.2 Exploratory Data Analysis
Start with question:
What is top 10 movie with big revenue? And please visualize it.
```{r}
top10 <- head(mv[order(mv$revenue, decreasing = TRUE), c("title", "revenue")], n = 10)
top10
rm(mv) #remove unused data to preserve memory
```

### 3.3 Data Visualization with ggplot2

```{r}
top10$title <- reorder(top10$title, as.numeric(top10$revenue))

# Formating in Billions
top10$revenue <- paste(format(round(top10$revenue / 1e9, 2), trim = TRUE), "B")

ggplot(top10, aes(title, revenue)) +
  geom_col(position = "dodge", aes(fill = revenue)) +
  coord_flip() +
  labs(x = "Movie Name", y = "Revenues in USD", title = "Top 10 Movie with Most Revenues All Time")

```

## 4. Final Thoughts
This is my first doing data visualization using Kaggle dataset

What I Learn?

* Doing pre-processing raw data
* Using lubridate() for date formatting
* Subsetting data based on column that will be used *title* and *revenue*
* Reordering data based on most revenue and limit it to 10 rows
* Formating revenue numeric values into **Billion(B)** format
* Data visualization with ggplot2 using `geom_col()` + `coord_flip()` + `labs()`

