---
title: "TMDB Movie - Data Visualisation"
author: "Enlik Tjioe"
date: "24 January 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r}
library(ggplot2)
library(GGally)
library(ggthemes)
library(ggpubr)
library(leaflet)
library(lubridate)
```

## Pre-Processing Data
Workflow:
* Reading your data
* Take a peek at your data
* Inspect your structure of data
* Formulate questions (strategic business value)
* Answer questions efficiently

Data Visualization Data (csv, database, images) -> preprocessing -> eda (exploratory data analysis) -> visualization / plotting

Core Techniques for EDA: `table() - table(insurance$gender)` for one-dimensional table - `table(insurance$gender, insurance$existingcust)` for 2-dimensional - `table("gender"=insurance$gender) - pie(table(x))`

xtabs() - Stands for cross-tabulation - format: `xtabs(formula=claims ~ category, data=insurance)` - by default, it uses the `sum()` as the breakdown - `plot(xtabs(x))`

aggregate() - In terms of format, very similar to xtabs except it takes an additional parameter - format: `xtabs(formula=claims ~ category, data=insurance, FUN=mean)` - If you find it useful, you can order the output by saving it as a `data.frame(x)`

### Pre-processing

```{r}
mv <- read.csv("data_input/tmdb_5000_movies.csv", stringsAsFactors = FALSE)
str(mv)

mv[,c("original_language", "status")] <- lapply(mv[,c("original_language", "status")], as.factor)
mv$release_date <- ymd(mv$release_date)
```

### Exploratory Data Analysis
```{r}

```


